Increasing the mortality gap? Social inequality in mortality among elderly and adults in Northern Sweden 1851--2013\footnote{Session "Health, morbidity, and mortality" at the Nordic Demographic Symposium 14--16 June 2017, Turku, Finland}

### 2017-10-09 article2.Rmd
fix some figures

```{r civstskum, fig.cap = "Exposure by marital status (from the top: never married, married and previously married) and time period", fig.height = 4.5}
xx <- with(skel, tapply(exposure, list(period = period, civst = civst), sum))
xy <- with(skume, tapply(exposure, list(period = period, civst = civst), sum))
xz <- with(foli, tapply(exposure, list(period = period, civst = civst), sum))
xxx <- rbind(xx, xy, xz)
yy <- round(prop.table(xxx, 1) * 100, 1)
barplot(t(yy)[3:1, ], col = c("red", "blue", "black"), las = 2, ylab = "Per cent")
```

>>>>

```{r civstskum, fig.cap = "Exposure by marital status (from the top: never married, married and previously married) and time period", fig.height = 4.5}
xx <- with(skel, tapply(exposure, list(period = period, civst = civst), sum))
xy <- with(skume, tapply(exposure, list(period = period, civst = civst), sum))
xz <- with(foli, tapply(exposure, list(period = period, civst = civst), sum))
xxx <- rbind(xx, xy, xz)
yy <- round(prop.table(xxx, 1) * 100, 1)
barplot(t(yy)[3:1, ], col = c("red", "blue", "green"), las = 2, ylab = "Per cent")
```

### 2017-10-09 cape.Rnw
fix some figures

>>>>

\begin{frame}{The sampling frame}

<<lexis2>>=
@

\begin{frame}{Exposure by social class, women}

\begin{center}
\includegraphics[height = 5cm]{figs/art2-hiscskumw-1}

\small From the top: Elite, middle, workers, missing.
\end{center}
\end{frame}

\begin{frame}{Exposure by social class, men}

\begin{center}
\includegraphics[height = 5cm]{figs/art2-hiscskumm-1}

\small From the top: Elite, middle, workers, missing.
\end{center}
\end{frame}

\begin{frame}{Exposure by marital status}

\begin{center}
\includegraphics[height = 5cm]{figs/art2-civstskum-1.pdf}

\small From the top: Never married, married, previously married.
\end{center}

\begin{frame}[fragile]{Cohort mortality, men 40--65}

<<cohortapproach>>=
vv <- vb0Tab[vb0Tab$cohort %in% seq(1751, 1951, by = 10) &
               vb0Tab$age %in% seq(40, 60, by = 5), ]
vv$age <- factor(vv$age)
vv$cohort <- factor(vv$cohort)
cohs <- levels(vv$cohort)
vv$age <- factor(vv$age)
n <- length(cohs)
coe <- matrix(0, nrow = 4, ncol = n)
for (i in 1:n){
   fit <- glm(event ~ offset(log(exposure)) + hisclass + age + urban + civst, 
              data = vv[vv$cohort == cohs[i] & vv$sex == "male", ],
              family = poisson)
   x <- coefficients(fit)[1:4]
   x[2:4] <- x[1] + x[2:4]
   coe[, i] <-  exp(x) / sum(exp(x))
}
x <- as.numeric(as.character(cohs))
par(lwd = 2)
plot(x[-n], coe[1, -n], type = "b", col = scol[1], ylim = c(0, 0.7), xlab = "Birth cohort", ylab = "Standardized rel. risks")
lines(x[-n], coe[2, -n], type = "b", col = scol[2], pch = 2, lty = 2)
lines(x[-n], coe[3, -n], type = "b", col = scol[3], pch = 3, lty = 3)
lines(x[-n], coe[4, -n], type = "b", col = scol[4], pch = 4, lty = 4)
legend("topleft", legend = c("elite", "middle", "worker", "NA"), pch = 1:4, col = scol, lty = 1:4)
@
